\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%############


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Ekjyot Singh Shinh} \\ \vspace{8pt}
    \small \href{mailto:ekjyotshinh@gmail.com}{\underline{ekjyotshinh@gmail.com}} $|$ 
    (916) 698-3435 $|$ 
    \href{https://linkedin.com/in/ekjyotshinh}{\underline{linkedin.com/in/ekjyotshinh}} $|$ 
    \href{https://github.com/ekjyotshinh}{\underline{GitHub}} $|$ 
    \href{https://ekjyotshinh.github.io}{\underline{Portfolio}} $|$ 
    Sacramento, CA
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {California State University, Sacramento}{Aug 2021 -- May 2025}
      {Bachelor of Science in Computer Science; GPA: 3.92/4.00}{}
  \resumeSubHeadingListEnd
  
  \vspace{-12pt}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Relevant Coursework:} Advanced Data Structures \& Algorithms, Parallel Programming (GPUs-CUDA), Advanced Database Management, Software Development, Operating Systems, Object-Oriented Programming, Computer Architecture \\
     \textbf{Certifications:} System Design (AlgoExpert), Machine Learning (AWS), Intro to Cloud (AWS), Intro to Generative AI (Udacity)
    }}
  \end{itemize}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Developer}{Feb 2024 -- Current}
      {Office of Water Programs}{Sacramento, CA}
      \resumeItemListStart
        \resumeItem{Engineered a secure checkout system integrating PayPal Expanded Checkout, handling \$45,000+ in daily transactions, ensuring data integrity, payment compliance and automated error reporting for faster issue resolution.}
        \resumeItem{Designed and developed a full online course delivery platform with enrollment authorization flow, lesson level access control, user progress tracking, Amazon S3-based file retrieval, and Redis caching for low-latency content delivery.}
        \resumeItem{Built an emailing microservice using a queue-based architecture with deferred sending and configurable retry logic, used across four client applications and multiple internal services to ensure reliable email delivery.}
        \resumeItem{Implemented secure JWT-based authentication, improving system security and ensuring reliable user session management.}
        \resumeItem{Rewrote UPS rate-fetching logic using multi-cURL parallelism, improving shipping rate retrieval speed by 75\%.}
        \resumeItem{Maintain and enhance production systems across PHP, Vue.js, Flask applications and internal microservices, contributing to continuous availability and feature expansion.}
      \resumeItemListEnd

    \resumeSubheading
      {Research Assistant}{Mar 2024 -- Current}
      {California State University, Sacramento}{Sacramento, CA}
      \resumeItemListStart
        \resumeItem{Optimized load balancing in a parallel Branch and Bound algorithm for the Sequential Ordering Problem (SOP) using a custom progress-based strategy, achieving a 15\% performance speedup.}
        \resumeItem{Leveraged Lin-Kernighan heuristic (LKH) entries for intelligent pruning, with early termination and reuse of the LKH thread within the solver, reducing execution time by 10\% and improving resource utilization.}
        \resumeItem{Developed a progress estimation metric to evaluate task progress, enabling comparative performance analysis across runs.}
      \resumeItemListEnd

    \resumeSubheading
      {Student Assistant (Math Mentor, Orientation Leader and Peer Mentor)}{Sept 2021 -- Feb 2024}
      {California State University, Sacramento}{Sacramento, CA}
      \resumeItemListStart
        \resumeItem{Mentored students in Linear Algebra, Calculus, and Pre-Calculus, breaking down complex concepts into clear explanations.}
        \resumeItem{Successfully led orientation sessions and presentations for 600+ new students while collaborating with 30 orientation leaders.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
        {\textbf{ChemTrack Mobile Application} \emph{(TypeScript, React Native, Go, Firestore, GCS, GCR)}}{}
        {\href{https://github.com/ekjyotshinh/ChemTrack}{\underline{GitHub}}}
        \resumeItemListStart
          \resumeItem{Led the development of a chemical inventory app for Encina High School, enabling accurate management of 500+ chemicals.}
          \resumeItem{Built a 3-tier RBAC model (Master/Admin/View), ensuring strong access boundaries and preventing unauthorized modification.}
          \resumeItem{Integrated Google Cloud Storage for storing and retrieving Safety Data Sheets, ensuring rapid access during emergencies.}
          \resumeItem{Incorporated QR code scanning to instantly fetch chemical metadata, reducing manual lookup time by an estimated 90\%.}
          \resumeItem{Implemented infinite scrolling using query pagination with Firestore cursor, reducing DB reads and improving UI performance.}
          \resumeItem{Set up a CI pipeline using GitHub Actions, automating test workflows and reducing manual QA efforts by 40\%.}
        \resumeItemListEnd
        
      \resumeProjectHeading
        {\textbf{Distributed Rate Limiter \& API Gateway} \emph{(Go, Redis, gRPC)}}{}
        {\href{https://github.com/ekjyotshinh/Rate-Limiter-API-Gateway}{\underline{GitHub}}}
        \resumeItemListStart
          \resumeItem{Engineered an API Gateway in Go supporting routing, JWT authentication, request validation, and centralized logging.}
          \resumeItem{Developed a standalone Rate Limiter using a Redis Lua-based atomic token-bucket algorithm, enforcing per-user and per-endpoint quotas across the system.}
          \resumeItem{Designed the architecture with gRPC based communication, Docker based deployment, and Redis backed state sharing to ensure consistent rate limiting across horizontally scaled API Gateway instances.}
        \resumeItemListEnd
        
      \resumeProjectHeading
        {\textbf{Lightweight Redis-like Key-Value Store} \emph{(Python, Sockets, Threads)}}{}
        {\href{https://github.com/ekjyotshinh/Lightweight-Redis-clone}{\underline{GitHub}}}
        \resumeItemListStart
          \resumeItem{Built a multithreaded in-memory key-value store with RESP protocol support, mutex-based thread safety, and key expiration.}
          \resumeItem{Added autosave/autoload for persistent storage, reducing cold start latency and ensuring data durability across server restarts.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages:} Python, JavaScript, Go, PHP, Java, C++, CUDA \\
     \textbf{Database:} MySQL, MSSQL, Firestore \\
     \textbf{Web Technologies:} React, Node.js, Gin, Docker, REST APIs, gRPC, Redis \\
     \textbf{Operating Systems:} Linux/UNIX, Windows \\
     \textbf{Tools:} Git, Visual Studio Code, Figma, Postman, Swagger, Jira, Kanban Board
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
